\myTitle

### 2024-07-10 002-GSI_and_Fst.Rmd
Done with major editing push

no_lfar_ass_table_80 <- top_ass$top %>% 
  filter(scaled_likelihood > 0.8) %>%
  plot_self_assignment_table(pop_labels, collection_order)

@@

lfar_ass_table_80 <- lfar_top_ass$top %>% 
  filter(scaled_likelihood > 0.8) %>%
  plot_self_assignment_table(pop_labels, collection_order)

@@

```{r}
over80 <- nrow(lfar_top_ass$top %>% filter(repu_sclike > 0.8))

lfar_top_ass$top %>% filter(repu_sclike > 0.8) %>% count(repunit == inferred_repunit) %>% mutate(fract = n / over80)
```

>>>>

no_lfar_ass_table_80 <- top_ass$top %>% 
  filter(repu_sclike > 0.8) %>%
  plot_self_assignment_table(pop_labels, collection_order)

@@

lfar_ass_table_80 <- lfar_top_ass$top %>% 
  filter(repu_sclike > 0.8) %>%
  plot_self_assignment_table(pop_labels, collection_order)

@@

Look at the distribution there:
```{r}
lfar_top_ass$top %>%
  filter(repunit != inferred_repunit) %>%
  count(collection, inferred_repunit)
```

Get some more values for the paper:

From CHLF to Fall
```{r}
lfar_top_ass$top %>%
  filter(collection == "CHLF") %>%
  count(repunit == inferred_repunit) %>%
  mutate(fract = n / sum(n))

From Fall to CHLF
```{r}
lfar_top_ass$top %>%
  filter(repunit == "CV-Fall") %>%
  count(repunit,inferred_repunit) %>%
  mutate(fract = n / sum(n))

```{r}
lfar_top_ass$top %>%
  filter(collection == "MDS") %>%
  count(repunit,inferred_repunit) %>%
  mutate(fract = n / sum(n))

#### Now, look at the >80% criterion.
```{r}
# first, the number and fraction of fish that are still assigned
lfar_top_ass$top %>% 
  mutate(gt80 = repu_sclike > 0.8) %>%
  count(gt80, repunit == inferred_repunit)
```

```{r}
lfar_top_80 <- lfar_top_ass$top %>% 
  filter(repu_sclike > 0.8)

lfar_top_80 %>%
  count(repunit == inferred_repunit) %>%
  mutate(fract = n / sum(n))
```

Drop the clear winter run strays
```{r}

lfar_top_80 %>%
  filter(!((inferred_collection == "SRW") & (inferred_repunit != repunit))) %>%
  count(repunit == inferred_repunit) %>%
  mutate(fract = n / sum(n))
```

And particularly look at misassignments to the CHLF and CV-Spring

From Fall to other repunits
```{r}
lfar_top_80 %>%
  filter(repunit == "CV-Fall") %>%
  count(repunit,inferred_repunit) %>%
  mutate(fract = n / sum(n))

### 2024-07-10 tex/body-text-of-paper.tex
Done with major editing push

The estimated pairwise $F_\mathrm{ST}$ values between the collections
varied from a low of 0.0 to a high of 0.288 (Figure~\ref{fig:gsi}a).
Notably, most of the largest values
of $F_\mathrm{ST}$ occurred between SRW and another collection.
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\newcommand{\gsicap}{\footnotesize Pairwise $F_\mathrm{ST}$ values and allele frequencies({\bf a)}
and self-assignment rates
 ({\bf b)}  for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  In ({\bf a}), for $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data. Each cell in the lower triangle shows a small scatter plot of estimated allele frequencies
in the collections---the $x$ value is allele frequencies from the collection in the column and the
$y$ value is from the collection in the row. Frequencies for all alleles are shown, with values within
each cell ranging from 0 to 1.  These frequencies were estimated by, for each locus, randomly
subsampling individuals from each collection to the minimum number of observed alleles in any collection
at the locus.  In ({\bf b}), for self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection.}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\gsicap]{\gsicap}
\label{fig:gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

Leave-one-out cross-validation (self-assignment) analysis demonstrates that this
reference baseline provides a high degree of accuracy for distinguishing the major
groups of Chinook salmon in California.  The results of the analysis are summarized
in a self-assignment matrix (Figure~\ref{fig:gsi}b).
This figure shows the collections divided into the seven different reporting groups:
SO-NCal-Coast,  Klamath-Trinity, Cent.\ Cal.\ Coast,
CV-Winter, CV-Spring, CV-Fall, and  CV-Late-Fall.  These groupings correspond
largely to the divisions in the data found by STRUCTURE, they also correspond
with divisions amongst the stocks as defined for management, and, as seen in the
figure, they correspond with groups of populations that can be reliably distinguished
from one another for population assignment.

Overall, of the 1613 fish in the reference baseline, 1587 (98.4\%) were correctly
assigned to their reporting unit of origin, while 26 (1.6\%) were incorrectly assigned.
Four of those 26 misassignments which involved fish being incorrectly assigned to
SRW, were clearly fish from SRW that had been incorrectly sampled into a different
collection, likely due to straying. (This is evident because SRW are so distinct that it is not possible
to incorrectly identify them).  Of the remaining 22 misassignments,  9 involved fish from the
CHLF (late fall run) collection being misassigned to the CV-Fall reporting unit and 7 were
fish from the MDS (Mill-Deer spring run) collection being assigned to the CV-Fall reporting unit.
It is possible that some of these misassignments represent CV-Fall fish that were incorrectly
sampled as CHLF or MDS; however, unlike with SRW, that we could not conclude that
confidently, as there is some degree of overlap in likelihood values between the two.

While fish from CHLF were found to misassign at a rate of 3.1\% (9/291) and MDS at a rate
of 8.6\% (7/81) to CV-Fall, are seen to misassign at fairly high rates to CV-Fall, the
converse is not evident---that is, fish from the CV-Fall are misassigned to CHLF at a rate
of only 0.6\% (3/501) and to the CV-Spring reporting unit (to which MDS belongs) at a rate
of only 0.4\% (2/501).

When assignments are only accepted with a scaled likelihood greater than 0.8,
18 assignments are discarded, but not all of those were incorrect.  At the 0.8 threshold,
the total fraction of correct assignments is 98.8\% (Fig.~\ref{fig:eighty}).

We note that the RoSA markers provide the differential signal necessary to distinguish the
Feather River spring-run stock from the other CCV stocks with a predominantly fall-run
genomic background, as they do not share genome-wide ancestry with the other spring-run
stocks/lineages in the basin. In this context, it is clear that the 'fall-run' hatchery
program in the Feather River both spawns and produces many spring-run fish and RoSA heterozygotes.
Similarly, in other regions, the RoSA markers are the only way to distinguish fall-
and spring-run fish, as they otherwise share genomic background.
In California, only the Sacramento and  Klamath basins have documented spring-run
salmon and their historical occurrence in other basins has been unclear. We find no
instance of spring-run fish in these coastal basins, but did identify one copy of the early-lineage
RoSA haplotype in the Eel River. Moreover, we identified three additional copies of a
recombinant haplotype that carries half of the RoSA SNPs from both the E and L lineages in the Eel and Russian rivers. No other clear recombinants were identified in the study populations, indicated that it arose in the California Coastal Chinook Salmon lineage, and provides further evidence of past presence of RoSA haplotypes associated with early migration.

@@

The results are summarized in Fig.~\ref{fig:fprs}.
%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\newcommand{\fprcap}{\footnotesize False positive rates (FPRs) as a function of false negative
rates (FNRs) for distinguishing between different relationships.  {\bf (a)} FPRs calculated
using importance sampling of unrelated pairs of individuals being incorrectly categorized as parent-offspring (PO),
full-sibling (FS) or half-sibling (HS) pairs.  {\bf (b)}  FPRs calculated using regular Monte Carlo
sampling of avuncular pairs (AN: aunt-niece, uncle-nephew, etc.) or full-siblings (FS) or half-siblings (HS) being
incorrectly categorized as parent-offspring (PO); as well as FPRs of parent-offspring (PO) pairs or half-sibling (HS)
pairs being incorrectly inferred as full siblings (FS).  In both {\em a} and {\em b}, 100,000 Monte Carlo replicates
were simulated.  Importance sampling allows estimation of very small false positive rates for unrelated pairs, but
cannot be applied to truly related pairs.  Consequently, it is difficult to accurately estimate small probabilities
($10^{-4}$ or less) in {\bf b}, as indicated by the error bars, which represent the estimate $\pm 2s$ where $s$
is the estimated standard error of the mean of the Monte Carlo sample.  This also is the reason that many of the lines terminate.   }
\begin{center}
\includegraphics[width=\textwidth]{images/fpr-fnr-figure-crop.pdf}
\end{center}
\caption[\fprcap]{\fprcap}
\label{fig:fprs}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%
And we can also point readers to the supplement figure \ref{fig:ckmr-comp}.
The power analyses for this set of markers demonstrate that they have ample variation
for accurate identification of parent-offspring (PO) and full-sibling (FS) pairs in almost all
realistic situations. The predicted false positive rates for both PO and FS pairs are
exceedingly low for even stringent false negative thresholds (e.g. 0.05).
For example, the false positive rate for FS identification is less than one error in 10 million
comparisons of potential siblings in the California Chinook salmon population with the lowest
heterozygosity (SRW) at a false negative rate of 0.05. However, HS pairs can not be accurately
distinguished from unrelated pairs in any populations without very large false negative rates
and in very modest-sized studies.
We note, however, that the presence in a dataset of genotypes from individuals that are related, but not in
 the relationship category proposed, will result in some additional misidentifications.
 These 'errors' will all involve related fish being identified as such, but in the incorrect relationship category.  The cross-assignment frequencies predicted for some common relationship categories, and for realistic FPR and FNR, are found in (Fig 4b).

\textbf{Although some additional errors might be
expected when related but non-FS individuals are sampled,  this number of comparisons exceeds
those necessary in almost all realistic scenarios.
We note that, as in previous work, it is nearly impossible to identify HS pairs accurately
with data from this, or any standard marker dataset. However, the use of properly LD-filtered
genome-scale data should allow such discrimination in future work.
Accurate relationship
inference in even the most genetically depauperate Chinook salmon population in California
and rangewide (Seeb et al. 2007, Clemento et al. 2014) is therefore possible with this marker set.}

@@

We describe a novel panel of microhaplotype genetic markers for Chinook salmon
in California that includes multiallelic gene regions with high variability for
relationship inference and gene regions identified in whole-genome sequence data
for increased power for population identification. We show how this set of markers
provides sufficient power for highly accurate identification of parent and offspring
pairs and full siblings in California Chinook salmon, and also allows near-perfect
identification of individuals to population or genetic group of origin. This set of
genetic markers lays the foundation for a comprehensive genetic monitoring and evaluation effort
that facilitates multiple types of inference and is flexible and extensible.
When, and if, sequencing costs drop sufficiently, it may be possible to include
all different populations of a single species within a single standardized reference baseline
that performs equally well at broad and regional scales. A statistical approach for population
assignment from low coverage whole genome sequences appeared recently
\citep{desaixINPRESSpopulation}, and its authors noted that such a data type could
be ideal for producing reference baselines simultaneously applicable to broad scale
coverage and high resolution within sub-regions.   For the present, however,
baselines tailored to specific regions are essential for regional management questions.

Although previous work using genome-scale data has shown that many of these populations or stocks can be resolved \cite{thompson2020complex,meek2020identifying},
such data is not practical for most large-scale applications of GSI and PBT, particularly because
of the much higher costs, longer turnaround time and challenges of producing highly
replicable datasets with reduced representation and low-coverage whole genome sequencing methods \cite{ali2016rad}.
Accurate identification of the distinct ecotypes of Chinook salmon in the California Central Valley is of utmost importance for designing and implementing effective conservation and management actions. This has been challenging, given the recent common ancestors of these ecotypes and ongoing migration between subbasins. We describe the first set of genetic markers that identifies the late-fall-run salmon ecotype, which occurs only in the CCV and shares a genomic background with the more common CCV fall-run salmon ecotype. Moreover, we show how the FRH spring-run lineage is easily identifiable through a combination of traditional GSI and the characterization of functional genetic markers in the RoSA. Finally, although previous work has described GSI capabilities that distinguish the natural-spawning CCV spring-run lineages from each other and their fall-run counterparts with moderately high accuracy, we demonstrate near complete accuracy in distinguishing these 'stocks'. Moreover, the few fish that are apparently misidentified (Fig. 3) are likely to be primarily migrants and not true misidentifications. For example, the three fish that were field-characterized as spring-run from Butte Creek, but are genetically identified as winter-run salmon are clearly carry the winter-run genomic background and could not realistically be misidentified on the basis of the genetic data. This marker set and baseline reference dataset also provides unprecedented power for identifying fish from not only the other ESUs in California, but even the individual populations within those ESUs (Fig. 3).
Additionally, previous genetic marker sets for California Chinook salmon had sufficient power for inferring parent-offspring relationships, but only when both parents were sampled and genotyped. This marker set considerably increases the capacity for relationship inference in California salmon, by providing sufficient power for parent-offspring relationship inference, when only one parent was sampled, as well as identifying pairs of full siblings when no parents are sampled. Groups of full siblings larger than two are identified even more accurately than expressed in Figure 4.

>>>>

The estimated pairwise $F_\mathrm{ST}$ values between the collections
varied from a low of 0.0 to a high of 0.288 (Figure~\ref{fig:gsi}a).
Notably, most of the largest values
of $F_\mathrm{ST}$ occurred between SRW and another collection.
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\newcommand{\gsicap}{\footnotesize Pairwise $F_\mathrm{ST}$ values and allele frequencies ({\bf a)}
and self-assignment rates
 ({\bf b)}  for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  In ({\bf a}), for $F_\mathrm{ST}$ values,
the upper triangle was computed using all the genetic markers except for those in the
RoSA on chromosome 28. 
Each cell in the lower triangle shows a small scatter plot of estimated allele frequencies
in the collections---the $x$ value is allele frequencies from the collection in the column and the
$y$ value is from the collection in the row. Frequencies for all alleles are shown, with values within
each cell ranging from 0 to 1.  These frequencies were estimated by, for each locus, randomly
subsampling individuals from each collection to the minimum number of observed alleles in any collection
at the locus.  In ({\bf b}), for self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection.
All individuals were assigned here, using a maximum-scaled-likelihood rule to reporting unit and
then to collection within reporting unit as described in the text. For the assignment matrix resulting
when only fish with a scaled likelihood $>0.80$ to reporting unit are assigned, see Figure~\ref{fig:eighty}}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\gsicap]{\gsicap}
\label{fig:gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

@@

Leave-one-out cross-validation (self-assignment) analysis demonstrates that this
reference baseline provides a high degree of accuracy for distinguishing the major
groups of Chinook salmon in California.  The results of the analysis are summarized
in a self-assignment matrix (Figure~\ref{fig:gsi}b).
This figure shows the collections divided into the seven different reporting groups:
SO-NCal-Coast,  Klamath-Trinity, Cent-Cal-Coast,
CV-Winter, CV-Spring, CV-Fall, and  CV-Late-Fall.  These groupings correspond
largely to the divisions in the data found by STRUCTURE, they also correspond
with divisions amongst the stocks as defined for management, and, as seen in the
figure, they correspond with groups of populations that can be reliably distinguished
from one another for population assignment.

Overall, of the 1636 fish in the reference baseline, 1612 (98.5\%) were correctly
assigned to their reporting unit of origin, while 24 (1.5\%) were incorrectly assigned.
Four of those 24 misassignments which involved fish being incorrectly assigned to
SRW, were clearly fish from SRW that had been incorrectly sampled into a different
collection, likely due to straying. (This is evident because SRW are so distinct that it is not possible
to incorrectly identify them).  Of the remaining 20 misassignments,  8 involved fish from the
CHLF (late fall run) collection being misassigned to the CV-Fall reporting unit and 6 were
fish from the MDS (Mill-Deer spring run) collection being assigned to the CV-Fall reporting unit.
It is possible that some of these misassignments represent CV-Fall fish that were incorrectly
sampled as CHLF or MDS; however, unlike with SRW,  we  cannot conclude that
confidently, as there is some degree of overlap in likelihood values between the two.

While fish from CHLF were found to misassign at a rate of 2.7\% (8/300) and MDS at a rate
of 7.1\% (6/84) to CV-Fall, the
converse is not evident---that is, fish from the CV-Fall are misassigned to CHLF at a rate
of only 0.6\% (3/508) and to the CV-Spring reporting unit (to which MDS belongs) at a rate
of only 0.4\% (2/508).

When assignments are only accepted with a scaled likelihood greater than 0.8,
20 assignments are discarded, and half of those (10) were the incorrect assignments.  Thus,
at the 0.8 threshold, the total fraction of correct assignments is 99.1\% (Fig.~\ref{fig:eighty}).
Notably with the $>0.8$ criterion, the misassignment rates from the abundant CV-Fall
reporting unit to CV-Late-Fall or to CV-Spring both drop below 0.2\% (1/502).

As seen in previous studies, FRHS, the Feather River Hatchery
spring-run stock, is considerably differntiated from the remaining spring-run
stocks in the Central Valley (MDS and BCS). This is reflected in the low
misassignment rates of FRHS fish to the CV-Spring, and is also evident in the
STRUCTURE results.   We note, however, that the RoSA markers provide
the differential signal necessary to distinguish
Feather River spring-migrating fish from the other CCV stocks with a predominantly fall-run
genomic background. This is evident when the assignment matrix is enumerated in
terms of RoSA genotypes (Figure~\ref{fig:rosa-gsi}). In this context, it is clear that the ``fall-run'' hatchery
program in the Feather River both spawns and produces many spring-run fish and RoSA heterozygotes.
Similarly, in other regions, such as the Trinity River, the RoSA markers are the only reliable means to distinguish fall-
and spring-run fish, as they otherwise share genomic background.

In California, only the Sacramento and  Klamath basins have documented spring-run
salmon and their historical occurrence in other basins has been unclear. We find no
instance of spring-run fish in these coastal basins, but did identify one copy of the early-lineage
RoSA haplotype in the Eel River. Moreover, we identified three additional copies of a
recombinant haplotype that carries half of the RoSA SNPs from both the E and L lineages in the Eel and Russian rivers. No other clear recombinants were identified in the study populations, indicating that it arose in the California Coastal Chinook Salmon lineage, and providing further evidence of past presence of RoSA haplotypes associated with early migration.

@@

The results are summarized in Fig.~\ref{fig:fprs}.
%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\newcommand{\fprcap}{\footnotesize False positive rates (FPRs) as a function of false negative
rates (FNRs) for distinguishing between different relationships.  {\bf (a)} FPRs calculated
using importance sampling of unrelated pairs of individuals being incorrectly categorized as parent-offspring (PO),
full-sibling (FS) or half-sibling (HS) pairs.  {\bf (b)}  FPRs calculated using regular Monte Carlo
sampling of avuncular pairs (AN: aunt-niece, uncle-nephew, etc.) or full-siblings (FS) or half-siblings (HS) being
incorrectly categorized as parent-offspring (PO); as well as FPRs of parent-offspring (PO) pairs or half-sibling (HS)
pairs being incorrectly inferred as full siblings (FS).  In both {\em a} and {\em b}, 100,000 Monte Carlo replicates
were simulated.  Importance sampling allows estimation of very small false positive rates for unrelated pairs, but
cannot be applied to truly related pairs.  Consequently, it is difficult to accurately estimate small probabilities
($10^{-4}$ or less) in {\bf b}, as indicated by the error bars, which represent the estimate $\pm 2s$ where $s$
is the estimated standard error of the mean of the Monte Carlo sample.  This also is the reason that many of the lines terminate.   }
\begin{center}
\includegraphics[width=\textwidth]{images/fpr-fnr-figure-crop.pdf}
\end{center}
\caption[\fprcap]{\fprcap}
\label{fig:fprs}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%

The `CKMRsim' power analyses for this set of markers demonstrates that they have ample variation
for accurate identification of parent-offspring (PO) and full-sibling (FS) pairs in almost all
realistic situations. The predicted false positive rates from unrelated pairs for both the
parent-offspring (PO) and full-sibling (FS) relationships are
exceedingly low for all population groups, even when using stringent false negative thresholds as
low as 0.05 (Fig.~\ref{fig:fprs}a).
For example, the false positive rate for FS identification is less than one error in 10 million
comparisons of potential siblings in the California Chinook salmon population with the lowest
heterozygosity (SRW) at a false negative rate of 0.05.

Half-sibling (HS) pairs cannot be accurately
distinguished from unrelated pairs in any populations without very large false negative rates
and in very modest-sized studies with very few pairwise comparisons.

In a reasonably large population, the vast majority of pairs of individuals are expected to
be unrelated, or at least, effectively unrelated, sharing common ancestors only many generations
in the past.  However, a small fraction of pairs will be more recently related, and distinguishing these
kin pairs from target relationships (like PO and FS) must be accounted for.  `CKMRsim' provides
facilities for assessing error rates between different kin groups, and results for these are
summarised in (Fig.~\ref{fig:fprs}b). Here, again, focusing on the results for the genetically
depauperate SRW, and using an FNR of 0.1 we see that the chance of incorrectly
categorizing an HS as an FS,  or an FS as a PO is less than 1 in 100. Likewise, 
we can expect PO to be misidentified as FS at a rate of around 1 in 500, and 
HS or Aunts/Uncles to be misidentified as parents at a rate less than 1 in 1000.
Though these rates are much higher than the FPRs for unrelated pairs, they should be
compared to the number of actual non-target kin pairs expected.  For example, in a salmon
population, the number of full aunts or uncles of a fish is unlikely to exceed 50, 
at later life stages,  so a FPR of  $<$0.001 is comfortably low in that case.

The presence of multiple alleles at many of these loci improves power for
kin inference compared to a marker panel using only a single SNP at each
amplicon.  To provide a visual display of the difference afforded by using
microhaplotypes compared to single SNPs in this data set, we show the
distribution of log-likelihood ratios for different relationships using our microhaplotype-scored
amplicons, versus using the most heterozygous single SNP from each
amplicon (\ref{fig:ckmr-comp}).  The figures show a considerable increase
in separation between the relationships categories from calling genotypes
as microhaplotypes in these amplicons.

@@

We describe a novel panel of microhaplotype genetic markers for Chinook salmon
in California that includes multiallelic gene regions with high variability for
relationship inference and gene regions identified in whole-genome sequence data
for increased power for population identification. We show how this set of markers
provides sufficient power for highly accurate identification of parent and offspring
pairs and full siblings in California Chinook salmon, and also allows near-perfect
identification of individuals to population or genetic group of origin. This set of
genetic markers lays the foundation for a comprehensive genetic monitoring and evaluation effort
that facilitates multiple types of inference and is flexible and extensible.

When, and if, sequencing costs drop sufficiently, it may be possible to include
all different populations of a single species within a single standardized reference baseline
that performs equally well at broad and regional scales. A statistical approach for population
assignment from low coverage whole genome sequences appeared recently
\citep{desaixINPRESSpopulation}, and its authors noted that such a data type could
be ideal for producing reference baselines simultaneously applicable to broad scale
coverage and high resolution within sub-regions.   For the present, however,
baselines tailored to specific regions are essential for regional management questions.

Although previous work using genome-scale data has shown that many of
these populations or stocks can be resolved \cite{thompson2020complex,meek2020identifying},
such data are not practical for most large-scale applications of GSI and PBT, particularly because
of the much higher costs, longer turnaround time and challenges of producing highly
replicable datasets with reduced representation and low-coverage whole genome sequencing methods \cite{ali2016rad}.

Accurate identification of the distinct ecotypes of Chinook salmon in the
California Central Valley is of utmost importance for designing and implementing
effective conservation and management actions. This has been challenging,
given the recent common ancestors of these ecotypes and ongoing migration between subbasins.
We describe the first replicable, reproducible panel of genetic markers that identifies the late-fall-run salmon ecotype,
which occurs only in the CCV and shares a genomic background with the more
common CCV fall-run salmon ecotype. Moreover, we show how the FRH spring-run lineage is
easily identifiable through a combination of traditional GSI and the characterization
of functional genetic markers in the RoSA. Finally, although previous work has described
GSI capabilities that distinguish the natural-spawning CCV spring-run lineages from
each other and their fall-run counterparts with moderately high accuracy, we demonstrate
near complete accuracy in distinguishing these 'stocks'. Moreover, the few fish that are
apparently misidentified (Fig. 3) are likely to be primarily migrants and not true misidentifications.
For example, the three fish that were field-characterized as spring-run from Butte Creek, but are
genetically identified as winter-run salmon clearly carry the winter-run genomic background and
are strays from the winter-run stock, as these 
could not realistically be misidentified on the basis of the genetic data.

This marker set and baseline reference dataset also provides
unprecedented power for identifying fish from not only the other ESUs in California,
but even the individual populations within those ESUs (Fig. 3).

Previous genetic marker sets for California Chinook salmon had sufficient power for inferring
parent-offspring relationships, but only when both parents were sampled and genotyped.
This marker set considerably increases the capacity for relationship inference in California
salmon, by providing sufficient power for parent-offspring relationship inference, when only
one parent is sampled, as well as identifying pairs of full siblings when no parents are sampled.
Groups of full siblings larger than two are identified even more accurately than expressed in Fig.~\ref{fig:fprs}.
Although some additional errors might be
expected when related but non-target kin pairs are sampled,  the false positive rates
for these non-targe kin pairs are sufficiently small
for almost all realistic scenarios.
Accurate relationship
inference in even the most genetically depauperate Chinook salmon population in California
and rangewide \citep{seeb2007development,clemento2014evaluation} is therefore possible with this marker set.
We note that, as in previous work, it is nearly impossible to identify HS pairs accurately
with data from this, or any standard marker dataset. Accurate identification of HS pairs
typically relies on thousands of SNP markers \citep{hillary2018genetic}.

### 2024-07-10 tex/supplemental-figures.tex
Done with major editing push

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{images/rosa-gsi-table-crop.pdf}
\end{center}
\caption[Assignment table by RoSA genotype]{\footnotesize Assignment table
like that in Fig.~\ref{fig:gsi}b in the paper, but with numbers according to genotypes
at the RoSA}
\label{fig:rosa-gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{images/rosa-gsi-table-crop.pdf}
\end{center}
\caption[Assignment table by RoSA genotype]{\footnotesize Assignment table
like that in Fig.~\ref{fig:gsi}b in the paper, but with numbers according to genotypes
at the RoSA. In each cell, the top left entry gives the number of EE (early run allele homozygotes)
genotypes, the middle entry is the number of EL genotypes (heterozygotes), and the bottom
right entry gives the number of LL (late-run homozygote) genotypes. }
\label{fig:rosa-gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
